\begin{rubric}{Work Experience}
\entry*[July 2023 -- Present]%
        \textbf{Web Manager} at Heuser \hfill\textbf{Karachi, PK}
        \par Initial Development of the website using Kajabi and Overseeing and managing online course platform, handling backend tasks like member management and content updates.
        
\entry*[Dec 2023 -- Present]%
	\textbf{Data Science Research Assistant} \hfill\textbf{London, UK}
        \par Collaborating on a Ph.D. research project, I lead data curation, collection, and cleaning efforts. Currently, I am developing Machine Learning models for effective analysis of sentiment in annual reports from 172 UK-based public companies. Tasks include predictive modeling with multiple variables and basic statistical analysis and EDA.
        
\entry*[April 2022 -- Present]%
        \textbf{Graphic Designer} \hfill\textbf{Freelance}
        \par Working as a freelance graphic designer specialising in Product Photo editing for ecommerce stores. 

\entry*[Aug 2020 -- April 2022]%
        \textbf{Teaching Assistant for Computer Science} at Cedar, Nixor, Sceptre \hfill\textbf{Karachi, PK}
        \par Collaborated with A-level Computer Science Teacher Sir Zain Merchant, assisting in the creation, checking, and management of assignments and tests. Organized weekly tutorial classes and actively engaged in teaching Python to students.

\entry*[June 2021 -- October 2021]%
        \textbf{Graphic Designer} at Vality Studio \hfill\textbf{Karachi, PK}
        \par Coming up with unique graphic designs for clients. Brainstorming innovative ideas for the company's official website. Worked along with the brand's content team.

\entry*[September 2019 -- March 2020]%
        \textbf{Peer Tutor Computer Science} at Cedar College \hfill\textbf{Karachi, PK}
        \par Appointed as official peer tutor for AL Computer Science at Cedar College. My tasks involved teaching and carrying out daily office hours to teach and solve any query related to the subject matter.
        
        
\end{rubric}